---
title: "Pre-Analytic Cleaning+Imputation"
output: html_document
date: "2025-06-17"
---

#Main Goal of This Script
Goal of This Is to Create our Predictor and Outcome Variables
- Predictors
    Demographics: Age, sex at birth, race, current SES, duration follow-up, pubertal status,
                  living w/ bio mother/father (dichotomized, currently 1-4).
                  
    Offspring Diagnosis: bipolar, unipolar, anxiety, adhd, behavior disorder, substance use     
                         disorders, psychoti disorders
                         
    Offspring Medication: antidepressants, antipsychotics, mood stabilizer, ADHD medications,                                 sedatives/hypnotics
    
    Parent Diagnosis: bipolar, unipolar depression, anxiety, ADHD, behavior disorder, substance use 
                      disorder, psychotic disorder
                      
    Sleep: Sleep predictors are added in a later stage.
    
- Outcomes
    Self-reported Symptoms: Depression, Affective Lability, Anxiety, ADHD, Psychotic Like       
                            Experiences.

    
#Capabilities of Code

To date this is the capabilities of this code
- Predictor Capabilities:
      - Youth Diagnosis is Finished
      - Demographics: Age, sex, & race are done. Duration follow-up, living status, and PDS need to 
                      be made.
      - Parent Diagnosis: Needs to be expanded to include anxiety, adhd, behavior, & SUD.
      - Offspring Medication Use: Untouched. 
      
- Outcome Capabilities:
      - Anxiety: Made standardized SCARED, can add SCAS.
      - Depression: Made standarized MFQ. 
      - ADHD Symptoms: CBCL untouched.
      - Psychotic-Like Symptoms: Need to work out how we are defining psychotic experiences with FF. Not a self-report. 
      - Affective Liability: CALS untouched. 



# Library
```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(haven); library(dplyr); library(tidyr); library(readr); library(readxl); library(data.table); library(stringr); library(purrr)  # Data manipulation & import
library(lme4); library(lmerTest); library(coxme); library(survival); library(broom); library(MuMIn); library(lsmeans)  # Modeling & statistics
library(pander); library(apaTables); library(flextable); library(officer); library(webshot2)  # Tables & reporting
library(ggplot2)  # Plotting
library(fuzzyjoin)  # Joins
library(survminer)
library(plotly)
```

## Load CSV
```{r}
# setwd("C:/Users/hubshmz/Documents/Code/git/data")  # FORBOW computer
setwd("C:/Users/zachh/Documents/Code/git/Data")  # Laptop
# setwd("C:/Users/zacha/Documents/RStudio/forbow/git/Data/ESCAP") # Tupper Windows Comp
# setwd("C:/Users/zacha/Documents/forbow/code/git") # Home Computer

FOR <- read.csv("rawdataforanalysis.csv", header=TRUE, fileEncoding="latin1")
```



#Outcome Creation
## Dimension Anxiety Creation
```{r}
Scared_C_Variables <- paste0("scared_child_", 1:41)
Scared_P_Variables <- paste0("scared_parent_", 1:41)
FOR <- FOR %>%
  # Recode 9s to NA
  mutate(across(all_of(Scared_C_Variables), ~na_if(.x, 9))) %>%
  mutate(across(all_of(Scared_P_Variables), ~na_if(.x, 9))) %>%
  
  # Compute total scores
  mutate(
    Scared_C_Total = rowSums(across(all_of(Scared_C_Variables)), na.rm = TRUE),
    Scared_P_Total = rowSums(across(all_of(Scared_P_Variables)), na.rm = TRUE)
  ) %>%
  
  # Standardize total scores
  mutate(
    Scared_C_Total_z = as.numeric(scale(Scared_C_Total)),
    Scared_P_Total_z = as.numeric(scale(Scared_P_Total))
  )

Scas_C_Variables <- paste0("scas_child_", 1:44)
Scas_P_Variables <- paste0("scas_parent_", 1:38)

remove_indices <- c(11, 17, 26, 31, 38, 43)
Scas_C_Variables <- Scas_C_Variables[-remove_indices]


# FOR <- FOR %>%
#   # Recode 9s to NA
#   mutate(across(all_of(Scas_C_Variables), ~na_if(.x, 9))) %>%
#   mutate(across(all_of(Scas_P_Variables), ~na_if(.x, 9))) %>%
#   
#   # Compute total scores
#   mutate(
#     Scas_C_Total = rowSums(across(all_of(Scas_C_Variables)), na.rm = TRUE),
#     Scas_P_Total = rowSums(across(all_of(Scas_P_Variables)), na.rm = TRUE)
#   ) %>%
#   
#   # Standardize total scores
#   mutate(
#     Scas_C_z = as.numeric(scale(Scas_C_Total)),
#     Scas_P_z = as.numeric(scale(Scas_P_Total))
#   )

FOR <- FOR %>%
  # SCAS dimanx
  mutate(dimanx = rowMeans(across(c(Scared_C_Total_z, Scared_P_Total_z)), na.rm = TRUE))
```

##Dimension Depression - MFQ
```{r}
ls(FOR, pattern = 'mfq')

mfq_C_Variables <- paste0("mfq_", sprintf("%02d", 1:13))
mfq_P_Variables <- paste0("mfq_p", 1:13)

FOR <- FOR %>%
  # Recode 9s to NA
  mutate(across(all_of(mfq_C_Variables), ~na_if(.x, 9))) %>%
  mutate(across(all_of(mfq_P_Variables), ~na_if(.x, 9))) %>%
  
  # Compute total scores
  mutate(
    mfq_C_Total = rowSums(across(all_of(mfq_C_Variables)), na.rm = TRUE),
    mfq_P_Total = rowSums(across(all_of(mfq_P_Variables)), na.rm = TRUE)
  ) %>%
  
  # Standardize total scores
  mutate(
    mfq_C_Total_z = as.numeric(scale(mfq_C_Total)),
    mfq_P_Total_z = as.numeric(scale(mfq_P_Total))
  )

FOR <- FOR %>%
  # MFQ dimdep
  mutate(dimdep = rowMeans(across(c(mfq_C_Total_z, mfq_P_Total_z)), na.rm = TRUE))
```

##Dimension ADHD?
Needs to be double checked
Chat about what we are looking for specifically. 
```{r}
ls(FOR, pattern = 'cbcl')

cbcl_vars <- c(
  "cbcl_042","cbcl_065","cbcl_069","cbcl_075","cbcl_080","cbcl_088","cbcl_102","cbcl_103","cbcl_111",
  "cbcl_051","cbcl_054","cbcl_056a","cbcl_056b","cbcl_056c","cbcl_056d","cbcl_056e","cbcl_056f","cbcl_056g",
  "cbcl_005","cbcl_012","cbcl_014","cbcl_031","cbcl_032","cbcl_033","cbcl_034","cbcl_035",
  "cbcl_045","cbcl_050","cbcl_052","cbcl_071","cbcl_089","cbcl_103","cbcl_112",
  "cbcl_002","cbcl_026","cbcl_028","cbcl_039","cbcl_043","cbcl_063","cbcl_067","cbcl_072","cbcl_081","cbcl_082","cbcl_090","cbcl_096","cbcl_099","cbcl_101",
  "cbcl_105","cbcl_106","cbcl_003","cbcl_007","cbcl_016","cbcl_019","cbcl_020","cbcl_021","cbcl_022","cbcl_023","cbcl_027","cbcl_037","cbcl_057","cbcl_068",
  "cbcl_074","cbcl_086","cbcl_087","cbcl_093","cbcl_094","cbcl_095","cbcl_097","cbcl_104",
  "cbcl_001","cbcl_004","cbcl_008","cbcl_010","cbcl_013","cbcl_017","cbcl_041","cbcl_045","cbcl_046","cbcl_061","cbcl_062","cbcl_078","cbcl_080",
  "cbcl_006","cbcl_015","cbcl_018","cbcl_024","cbcl_028","cbcl_029","cbcl_030","cbcl_036","cbcl_044","cbcl_047","cbcl_049","cbcl_053","cbcl_056h",
  "cbcl_058","cbcl_059","cbcl_060","cbcl_073","cbcl_076","cbcl_077","cbcl_079","cbcl_083","cbcl_091","cbcl_092","cbcl_098","cbcl_100","cbcl_107","cbcl_108","cbcl_109","cbcl_110"
)

FOR <- FOR %>%
  mutate(across(all_of(cbcl_vars), ~na_if(.x, 9))) %>%
  mutate(CBCL_total = rowSums(across(all_of(cbcl_vars))), na.rm = TRUE)
table(FOR$CBCL_total, useNA = ('always'))



# * cbcl total score
# alpha CBCL_042 CBCL_065 CBCL_069 CBCL_075 CBCL_080 CBCL_088 CBCL_102 CBCL_103 CBCL_111 CBCL_051 CBCL_054 CBCL_056a CBCL_056b ///
# CBCL_056c CBCL_056d CBCL_056e CBCL_056f CBCL_056g CBCL_005 CBCL_012 CBCL_014 CBCL_031 CBCL_032 CBCL_033 CBCL_034 CBCL_035 ///
# CBCL_045 CBCL_050 CBCL_052 CBCL_071 CBCL_089 CBCL_103 CBCL_112 ///
#  CBCL_002 CBCL_026 CBCL_028 CBCL_039 CBCL_043 CBCL_063 CBCL_067 CBCL_072 CBCL_081 CBCL_082 CBCL_090 CBCL_096 CBCL_099 CBCL_101 ///
#  CBCL_105 CBCL_106 CBCL_003 CBCL_007 CBCL_016 CBCL_019 CBCL_020 CBCL_021 CBCL_022 CBCL_023 CBCL_027 CBCL_037 CBCL_057 CBCL_068 ///
#  CBCL_074 CBCL_086 CBCL_087 CBCL_093 CBCL_094 CBCL_095 CBCL_097 CBCL_104 ///
#  CBCL_001 CBCL_004 CBCL_008 CBCL_010 CBCL_013 CBCL_017 CBCL_041 CBCL_045 CBCL_046 CBCL_061 CBCL_062 CBCL_078 CBCL_080 ///
#  CBCL_006 CBCL_015 CBCL_018 CBCL_024 CBCL_028 CBCL_029 CBCL_030 CBCL_036 CBCL_044 CBCL_047 CBCL_049 CBCL_053 CBCL_056h ///
#  CBCL_058 CBCL_059 CBCL_060 CBCL_073 CBCL_076 CBCL_077 CBCL_079 CBCL_083 CBCL_091 CBCL_092 CBCL_098 CBCL_100 CBCL_107 CBCL_108 CBCL_109 CBCL_110 ///
```

##Dimensions Psychotic
This one will require more work, as there are many things that contribute to funnyfeelings. Such as if it is distressing, psychotic, severe, etc.

CURRENTLY THIS WILL TREAT PROBABLE OR DEFINITE PLE AS == 1, ELSE 0. 
```{r}
FOR <- FOR %>%
  mutate(
    experiencedFF = if_else(
      if_any(c(ffy1_ple, ffy3_ple, ffy5_ple, ffy7_ple, 
               ffy9_ple, ffy11_ple, ffy13_ple), 
             ~ .x %in% c(2, 3)), 
      1L, 0L
    )
  )

table(FOR$experiencedFF)
```

##Dim Affection Lability
```{r}
ls(FOR, pattern = 'cals')

cals_c_var <- paste0("cals_", 1:20)
cals_p_var <- paste0("cals_pr_", 1:20)

FOR <- FOR %>%
  mutate(across(all_of(cals_c_var), ~na_if(.x, 9))) %>%
  mutate(across(all_of(cals_p_var), ~na_if(.x, 9))) %>%
  mutate(CBCL_total = rowSums(across(all_of(cals_c_var))), na.rm = TRUE) %>%
  mutate(CBCL_total = rowSums(across(all_of(cals_p_var))), na.rm = TRUE) %>%  
  mutate(
    mfq_C_Total_z = as.numeric(scale(mfq_C_Total)),
    mfq_P_Total_z = as.numeric(scale(mfq_P_Total))
  )
  

```



#Predictors
##Demographics
###Age
```{r}
FOR$assessment_date <- as.Date(FOR$assessment_date)
FOR$dob <- as.Date(FOR$dob)
FOR$age_days <- FOR$assessment_date - FOR$dob
FOR$age <- as.numeric(FOR$age_days) / 365.25
```

####Sex
```{r}
FOR <- FOR %>%
  group_by(subject_id) %>%
  mutate(dob = dob[which(is.na(time_point))][1]) %>%
  ungroup()
FOR <- FOR %>%
  group_by(subject_id) %>%
  mutate(sex = sex[which(is.na(time_point))][1]) %>%
  ungroup()
FOR <- FOR %>%
  mutate(sex = case_when(
    sex == 1 ~ 0,
    sex == 2 ~ 1
  ))
FOR <- FOR %>%
  group_by(subject_id) %>%
  filter(all(!is.na(dob) & dob != "")) %>%  # Keep only groups where *all* dob are not missing or empty
  ungroup()
invalid_si <- c("9999999888", "9999999998")
FOR <- FOR %>%
  filter(!subject_id %in% invalid_si)
```

###Race?


##Parent Diagnosis and Family Risk
```{r}
FOR$fid <- substr(FOR$subject_id, 5, 7)
FOR$iid <- substr(FOR$subject_id, 8, 11)
FOR_P <- FOR %>%
  filter(str_detect(subject_id, "F[1-3]|f[1-3]|M[1-3]|m[1-3]|\\$R"))


FOR_P <- FOR_P %>%
  mutate(group = case_when(
    mdx == 4 ~ 1,
    mdx %in% c(2, 3) ~ 2,
    mdx == 1 ~ 3,
    mdx == 0 ~ 0,
    fdx == 4 ~ 1, 
    fdx %in% c(2,3) ~ 2,
    fdx == 1 ~ 3,
    fdx == 0 ~ 0,
    TRUE ~ NA_real_
  ))

FOR_P <- FOR_P %>%
  group_by(subject_id) %>%
  mutate(
    group = {
      g <- group[is.na(time_point)]
      if (length(g) == 0 || is.na(g[1])) 0 else g[1]
    }
  ) %>%
  ungroup()


#Pure exploratory to see what kind of group combos we have 
fid_groups <- FOR_P %>%
  distinct(fid, group) %>%
  group_by(fid) %>%
  summarise(groups = list(sort(unique(group))), .groups = "drop")
fid_groups <- fid_groups %>%
  mutate(group_combo = sapply(groups, paste, collapse = "-"))
combo_summary <- fid_groups %>%
  count(group_combo) %>%
  arrange(desc(n))

print(combo_summary)
```

##Medication
```{r}
med_vars <- c("med1_pick", "med2_pick", "med3_pick", "med4_pick", "med5_pick", "med6_pick", "med7_pick")

FORt <- FOR %>%
  mutate(across(all_of(med_vars), tolower))

#antidepressants
##

#antipsychotics 
##

#mood stabilizer 
##

#ADHD medications
#sedatives/hypnotics

##-------------- SIDE WORK ---------------

#Vitamins and Supplements
##melatonin
#'vitamin/vitamins'
#fish oil

#Insulin? Diabetes


#Birth Control/Contraceptives


FORt <- FORt %>%
  mutate(
    VitOrSupp = ifelse(
      apply(select(., all_of(med_vars)) %in% c("melatonin", "gummies", "vitamin", "vitamins"), 
            1, any),
      1, 0
    )
  )

#Analgesics
##Tylenol

#Dev
list <- FORt$med1_pick

list <- list[ !str_detect(list, "^$") ]
head(list, 50)

list <- list[!str_detect(list, "melatonin")]
list <- list[!str_detect(list, "gummies")]
list <- list[!str_detect(list, "vitamin")]
head(list, 50)


#1282 left. 



```

##Diagnosises
###Current Diagnosis
```{r}
### List of FORBOW Diagnoses


KSADS_ALL <- c('MDD', 'DEP', 'Dysthy', 'BP', 'BPI', 'BPII', 'MOOD',
               'Psychosis', 'iPsychosis', 'SCZ', 'SchAff',
               'SUD', 'Alc', 'Can', 'Dependence',
               'Anx', 'Panic', 'OthAnx', 'GAD', 'SocialP', 'PTSD', 'Agora', 'SpecificP', 'OCD', 'SAD',
               'ADHD', 'ODD', 'Conduct', 'Disrupt',
               'ED', 'EDNOS', 'Anor', 'Bulims',
               'Autism', 'ASD', 'Tic', 'Touret',
               'LD', 'LDs', 'LDg',
               'DMDD', 'Sleep',
               'Borderline', 'Antisocial', 'PersonalityDisord')


##ccMDD = 0
##ccDEP = 0
##ccPsychosis = 0
##cciPsychosis = 0
##ccSCHZ = 0
##ccSchAff = 0 
##ccBPD = 0
##ccBPDI = 0
##ccBPDII = 0
##ccBorderline = 0
##ccAntisocial = 0
##ccANX = 0
##ccPanic = 0
##ccOthAnx = 0
##ccGAD = 0
##ccSocialP = 0 
##ccAgora = 0
##ccPTSD = 0 
##ccOCD = 0
##ccSAD = 0
##ccSpecificP = 0
##ccSUD = 0
##ccCan = 0
##ccAlc = 0
##ccDependence = 0
##ccADHD = 0
##ccODD = 0
##ccConduct = 0
##ccDisrupt = 0
##ccED = 0
##ccAnor = 0
##ccBulim = 0
##ccEDNOS = 0
##ccAutism = 0
##ccASD = 0
##ccTic = 0
##ccTouret = 0
##ccLD = 0
##ccLDs = 0
##ccLDg = 0
##ccSleep
##ccDMDD
##ccDysthy = 0

###Varaibles we have but are unused?
#ccPBPD = 0
#ccPDD = 0
#ccAdjAnx = 0



##Clinical Diagnosis from Consesus
Diagnosis_vars <- paste0("cd_c_dx_", 1:10)

#Depression
FOR$ccMDD <- 0
FOR$ccDEP <- 0 
FOR$ccDysthy <- 0
for (i in 1:10) {
  dx_col <- paste0("cd_c_dx_", i)
  conf_col <- paste0("cd_c_confirmed_", i)
  text_col <- paste0("cd_c_dx_other_", i)
  rows_to_update <- FOR[[dx_col]] == 1 & FOR[[conf_col]] != 0
  FOR$ccMDD[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(1,2,3) & FOR[[conf_col]] != 0
  FOR$ccDEP[rows_to_update] <- 1
  rows_to_update <- FOR[[text_col]] %in% c("depress", "Depress", "Major Depress", "major depress") & FOR[[conf_col]] != 0
  FOR$ccDEP[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(2) & FOR[[conf_col]] != 0
  FOR$ccDysthy[rows_to_update] <- 1
}

#Mania
FOR$ccBP <- 0
FOR$ccBPI <- 0
FOR$ccBPII <- 0
for (i in 1:10) {
  dx_col <- paste0("cd_c_dx_", i)
  conf_col <- paste0("cd_c_confirmed_", i)
  text_col <- paste0("cd_c_dx_other_", i)
  rows_to_update <- FOR[[dx_col]] %in% c(4, 5,6,7) & FOR[[conf_col]] != 0
  FOR$ccBP[rows_to_update] <- 1
  rows_to_update <- FOR[[dx_col]] %in% c(4) & FOR[[conf_col]] != 0
  FOR$ccBPI[rows_to_update] <- 1
  rows_to_update <- FOR[[dx_col]] %in% c(5) & FOR[[conf_col]] != 0
  FOR$ccBPI[rows_to_update] <- 1
  rows_to_update <- FOR[[text_col]] %in% c("Mania", "mania", "Bipolar", "bipolar") & FOR[[conf_col]] != 0
  FOR$ccBP[rows_to_update] <- 1
}
table(FOR$ccBP)
table(FOR$ccBPI)
table(FOR$ccBPII)


##Psychosis
FOR$ccPsychosis <- 0
FOR$cciPsychosis <- 0
FOR$ccSCZ <- 0
FOR$ccSchAff <- 0
for (i in 1:10) {
  dx_col <- paste0("cd_c_dx_", i)
  conf_col <- paste0("cd_c_confirmed_", i)
  rows_to_update <- FOR[[dx_col]] %in% c(8,9,10,11,12,13,14) & FOR[[conf_col]] != 0 
  FOR$ccPsychosis[rows_to_update] <- 1
  rows_to_update <- FOR[[dx_col]] %in% c(8) & FOR[[conf_col]] != 0 
  FOR$ccSCZ[rows_to_update] <- 1
  rows_to_update <- FOR[[dx_col]] %in% c(9) & FOR[[conf_col]] != 0 
  FOR$ccSchAff[rows_to_update] <- 1
}

#Personality
FOR$ccBorderline <- 0
FOR$ccAntisocial <- 0
FOR$ccPersonalityDisord <- 0
for (i in 1:10) {
  dx_col <- paste0("cd_c_dx_", i)
  conf_col <- paste0("cd_c_confirmed_", i)
  text_col <- paste0("cd_c_dx_other_", i)
  rows_to_update <- FOR[[dx_col]] %in% c(25) & FOR[[conf_col]] != 0 
  FOR$ccBorderline[rows_to_update] <- 1
  rows_to_update <- FOR[[text_col]] %in% c("orderline") & FOR[[conf_col]] != 0
  FOR$ccBorderline[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(26) & FOR[[conf_col]] != 0 
  FOR$ccAntisocial[rows_to_update] <- 1
  rows_to_update <- FOR[[text_col]] %in% c("ntisocial") & FOR[[conf_col]] != 0
  FOR$ccAntisocial[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(70,71,72,73,74,75,76,77,78,79,80) & FOR[[conf_col]] != 0
  FOR$ccPersonalityDisord[rows_to_update] <- 1
  rows_to_update <- FOR[[text_col]] %in% c("personality", "Personality", "antisocial", "Antisocial", "orderline") &FOR[[conf_col]] != 0
  FOR$ccPersonalityDisord[rows_to_update] <- 1
}

#Substance Use
FOR$ccAlc <- 0
FOR$ccCan <- 0
FOR$ccSUD <- 0
FOR$ccDependence <- 0
for (i in 1:10) {
  dx_col <- paste0("cd_c_dx_", i)
  conf_col <- paste0("cd_c_confirmed_", i)
  rows_to_update <- FOR[[dx_col]] %in% c(38,39) & FOR[[conf_col]] != 0 
  FOR$ccAlc[rows_to_update] <- 1
  rows_to_update <- FOR[[dx_col]] %in% c(40,41) & FOR[[conf_col]] != 0 
  FOR$ccCan[rows_to_update] <- 1
  rows_to_update <- FOR[[dx_col]] %in% c(38,39,40,41,42,43) & FOR[[conf_col]] != 0 
  FOR$ccSUD[rows_to_update] <- 1
  rows_to_update <- FOR[[dx_col]] %in% c(39,41,43) & FOR[[conf_col]] != 0 
  FOR$ccDependence[rows_to_update] <- 1
}

#Anxiety Disorders
FOR$ccAnx <- 0
FOR$ccSAD <- 0  #Why is SAD 15 and why is anxiety within SAD?
FOR$ccSpecificP <- 0
FOR$ccSocialP <- 0 
FOR$ccAgora <- 0
FOR$ccPanic <- 0
FOR$ccGAD <- 0
FOR$ccOCD <- 0
FOR$ccPTSD <- 0
FOR$ccOthAnx <- 0
for (i in 1:10) {
  dx_col <- paste0("cd_c_dx_", i)
  conf_col <- paste0("cd_c_confirmed_", i)
  text_col <- paste0("cd_c_dx_other_", i)
  
  rows_to_update <- FOR[[dx_col]] %in% c(15,16,17,18,19,20,21,22,24) & FOR[[conf_col]] != 0    #Anxiety Disorders
  FOR$ccAnx[rows_to_update] <- 1
  rows_to_update <- FOR[[text_col]] %in% c("nxiety", "GAD", "Mutism", "mutism") & FOR[[conf_col]] != 0    #Anxiety disorders
  FOR$ccAnx[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(15) & FOR[[conf_col]] != 0    #SAD?
  FOR$ccSAD[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(16) & FOR[[conf_col]] != 0   #Specific P
  FOR$ccSpecificP[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(17) & FOR[[conf_col]] != 0   #Social P
  FOR$ccSocialP[rows_to_update] <- 1
  rows_to_update <- FOR[[text_col]] %in% c("Social") & FOR[[conf_col]] != 0 #Social P
  FOR$ccSocialP[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(18) & FOR[[conf_col]] != 0        #AGORA
  FOR$ccAgora[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(19) & FOR[[conf_col]] != 0       #Panic
  FOR$ccPanic[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(20) & FOR[[conf_col]] != 0       #GAD
  FOR$ccGAD[rows_to_update] <- 1
  rows_to_update <- FOR[[text_col]] %in% c("GAD") & FOR[[conf_col]] != 0 #GAD
  FOR$ccGAD[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(21) & FOR[[conf_col]] != 0       #OCD
  FOR$ccOCD[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(22) & FOR[[conf_col]] != 0       #PTSD
  FOR$ccPTSD[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(24) & FOR[[conf_col]] != 0       #OthAnx
  FOR$ccOthAnx[rows_to_update] <- 1
}

#Eating Disorder
FOR$ccAnor <- 0
FOR$ccBulims <- 0
FOR$ccEDNOS <- 0
FOR$ccED <- 0
for (i in 1:10) {
  dx_col <- paste0("cd_c_dx_", i)
  conf_col <- paste0("cd_c_confirmed_", i)
  text_col <- paste0("cd_c_dx_other_", i)
  
  rows_to_update <- FOR[[dx_col]] %in% c(28) & FOR[[conf_col]] != 0 
  FOR$ccAnor[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(29) & FOR[[conf_col]] != 0 
  FOR$ccBulims[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(30) & FOR[[conf_col]] != 0 
  FOR$ccEDNOS[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(28,29,30) & FOR[[conf_col]] != 0 
  FOR$ccED[rows_to_update] <- 1
  rows_to_update <- FOR[[text_col]] %in% c("Eating","eating","Pica", "pica") & FOR[[conf_col]] != 0 
  FOR$ccED[rows_to_update] <- 1
}

##Development
FOR$ccADHD <- 0
FOR$ccODD <- 0
FOR$ccConduct <- 0
FOR$ccDisrupt <- 0
for (i in 1:10) {
  dx_col <- paste0("cd_c_dx_", i)
  conf_col <- paste0("cd_c_confirmed_", i)
  text_col <- paste0("cd_c_dx_other_", i)
  
  rows_to_update <- FOR[[dx_col]] %in% c(31,32,33) & FOR[[conf_col]] != 0    #ADHD
  FOR$ccADHD[rows_to_update] <- 1
  rows_to_update <- FOR[[text_col]] %in% c("ADHD") & FOR[[conf_col]] != 0 
  FOR$ccADHD[rows_to_update] <- 1
    
  rows_to_update <- FOR[[dx_col]] %in% c(34) & FOR[[conf_col]] != 0         #ODD
  FOR$ccODD[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(35) & FOR[[conf_col]] != 0        #Conduct
  FOR$ccConduct[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(34,35) & FOR[[conf_col]] != 0        #Disruptive Disorder
  FOR$ccDisrupt[rows_to_update] <- 1
  rows_to_update <- FOR[[text_col]] %in% c("isruptive") & FOR[[conf_col]] != 0 
  FOR$ccDisrupt[rows_to_update] <- 1
}

#Neuro
FOR$ccTic <- 0
FOR$ccTouret <- 0
FOR$ccAutism <- 0
FOR$ccASD <- 0
for (i in 1:10) {
  dx_col <- paste0("cd_c_dx_", i)
  conf_col <- paste0("cd_c_confirmed_", i)
  text_col <- paste0("cd_c_dx_other_", i)
  
  rows_to_update <- FOR[[dx_col]] %in% c(36,37) & FOR[[conf_col]] != 0    #TIC
  FOR$ccTic[rows_to_update] <- 1
  rows_to_update <- FOR[[text_col]] %in% c("Tic", "tic", "ouret") & FOR[[conf_col]] != 0 
  FOR$ccTic[rows_to_update] <- 1
    
  rows_to_update <- FOR[[dx_col]] %in% c(36) & FOR[[conf_col]] != 0         #Touret
  FOR$ccTouret[rows_to_update] <- 1
  rows_to_update <- FOR[[text_col]] %in% c("ouret") & FOR[[conf_col]] != 0 
  FOR$ccTouret[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(44) & FOR[[conf_col]] != 0        #Autism
  FOR$ccAutism[rows_to_update] <- 1
  
  rows_to_update <- FOR[[dx_col]] %in% c(44,45, 46) & FOR[[conf_col]] != 0        #Autism Spectrum
  FOR$ccASD[rows_to_update] <- 1
}

#Learning Disabilities
FOR$ccLD <- 0
FOR$ccLDs <- 0
FOR$ccLDg <- 0
for (i in 1:10) {
  dx_col <- paste0("cd_c_dx_", i)
  conf_col <- paste0("cd_c_confirmed_", i)
  text_col <- paste0("cd_c_dx_other_", i)
  
  rows_to_update <- FOR[[text_col]] %in% c("LD", "Learning", "learning", "Intellectual", "intellectual", "Fragile", "Dyslexia", "dyslexia", "Dysgraphia", "dysgraphia", "Retardation", "retardation", "Communication", "disability")
  FOR$ccLD[rows_to_update] <- 1
    
  rows_to_update <- FOR[[text_col]] %in% c("Spelling", "spelling", "Reading", "reading", "Non-Verbal", "Processing Speed", "Phonological", "Dyslexia", "dyslexia", "dysgraphia", "Dysgraphia", "Communication") 
  FOR$ccLDs[rows_to_update] <- 1
  
  rows_to_update <- FOR[[text_col]] %in% c("Intellectual", "intellectual", "Retardation", "retardation") 
  FOR$ccLDs[rows_to_update] <- 1
}

#Sleep
FOR$ccSleep <- 0
for (i in 1:10) {
  dx_col <- paste0("cd_c_dx_", i)
  conf_col <- paste0("cd_c_confirmed_", i)
  text_col <- paste0("cd_c_dx_other_", i)
  rows_to_update <- FOR[[text_col]] %in% c("insomnia", "sleep", "somnia")
  FOR$ccSleep[rows_to_update] <- 1
}


#Disruptive Mood
FOR$ccDMDD <- 0
for (i in 1:10) {
  dx_col <- paste0("cd_c_dx_", i)
  conf_col <- paste0("cd_c_confirmed_", i)
  text_col <- paste0("cd_c_dx_other_", i)
  rows_to_update <- FOR[[text_col]] %in% c("DMDD")
  FOR$ccDMDD[rows_to_update] <- 1
}

FOR <- FOR %>%
  mutate(ccMOOD = ifelse(ccBP == 1 | ccDEP == 1 | ccMDD == 1, 1, 0))



for (i in KSADS_ALL) {
  dx_col <- paste0("cc", i)
  
  for (x in 1:16) {
    nxt_col <- paste0(i, "NxtYr", x)
    prv_col <- paste0(i, "PrvYr", x)
    
    FOR <- FOR %>%
      group_by(subject_id) %>%
      arrange(desc(time_point)) %>%
      mutate(
        !!nxt_col := lag(.data[[dx_col]], x),
        !!prv_col := lead(.data[[dx_col]], x)
      ) %>%
      ungroup()
  }
}


for (i in KSADS_ALL) {
  FOR[[paste0("FutureDiag", i)]] <- 0
  FOR[[paste0("PastDiag", i)]] <- 0
}

# Step 2: Loop through each diagnosis and lag/lead year
for (i in KSADS_ALL) {
  for (x in 1:16) {
    dx_Nxt_col <- paste0(i, 'NxtYr', x)
    dx_Prv_col <- paste0(i, 'PrvYr', x)
    future_col <- paste0('FutureDiag', i)
    past_col <- paste0('PastDiag', i)

    # If the future column exists and has value 1
    if (dx_Nxt_col %in% names(FOR)) {
      idx <- which(FOR[[dx_Nxt_col]] == 1)
      FOR[[future_col]][idx] <- 1
    }

    # If the past column exists and has value 1
    if (dx_Prv_col %in% names(FOR)) {
      idx <- which(FOR[[dx_Prv_col]] == 1)
      FOR[[past_col]][idx] <- 1
    }
  }
}

```


###Lifetime Diagnosis
```{r}
###Lifetime Diagnosis
#List of lifetime diagnosis  missing?

#clPBPD, clPDD, clAdjAnx, clPrim

##Mood

for (dx in KSADS_ALL) {
  cc_var <- paste0("cc", dx)
  cl_var <- paste0("cl", dx)

  FOR <- FOR %>%
    group_by(subject_id) %>%
    arrange(assessment_date, .by_group = TRUE) %>%
    mutate(!!cl_var := as.integer(cumsum(.data[[cc_var]] == 1) > 0)) %>%
    ungroup()
}
table(FOR$clMDD)
```


###Onset
```{r}
KSADS <- c('MDD', 'BP', 'BPI', 'BPII', 'MOOD', 'Psychosis', 'SCZ', 'SchAff', 'iPsychosis', 'SUD', 'Alc', 'Can', 'Dependence', 'Anx', 'Panic', 'OthAnx', 'GAD', 'SocialP', 'PTSD', 'Agora', 'OCD', 'SAD', 'ADHD', 'ODD', 'Conduct', 'Disrupt', 'ED', 'EDNOS', 'Anor', 'Bulims', 'Autism', 'ASD', 'Tic', 'Touret', 'LD', 'LDs', 'LDg', 'DMDD', 'Sleep', 'Borderline', 'Antisocial', 'PersonalityDisord')

for (dx in KSADS) {
  cc_var <- paste0("cc", dx)
  o_var <- paste0("o", dx)

  FOR <- FOR %>%
    group_by(subject_id) %>%
    arrange(assessment_date, .by_group = TRUE) %>%
    mutate(!!o_var := ifelse(row_number() == which(.data[[cc_var]] == 1)[1] & .data[[cc_var]] == 1, 1, 0)) %>%
    ungroup()
}
```

###Hospital Diagnosis
```{r}
###  Diagnosis from IWK, notes, conseus
FOR$iid <- substr(FOR$subject_id, 10,12)
FOR$iid <- as.numeric(FOR$iid)
#Originally ccCan was cannabis, should this be different?
FOR <- FOR %>%
  mutate(
    ccSUD = ifelse(iid == 443 & time_point %in% c(2, 3), 1, ccSUD),
    ccCan = ifelse((iid == 443 & time_point == 3) |
                      (iid == 321 & time_point %in% c(3, 4, 5)), 1, ccCan),
    ccPsychosis = ifelse((iid == 443 & time_point == 3) |
                         (iid == 281 & time_point == 5), 1, ccPsychosis),
    clSUD = ifelse((iid == 321 & time_point == 5) |
                   (iid == 443 & time_point %in% c(2, 3)), 1, clSUD),
    ccBorderline = ifelse(iid == 321 & time_point == 5, 1, ccBorderline),
    clBorderline = ifelse(iid == 321 & time_point == 5, 1, clBorderline),
    ccAntisocial = ifelse(iid == 321 & time_point == 5, 1, ccAntisocial),
    clAntisocial = ifelse(iid == 321 & time_point == 5, 1, clAntisocial),
    clPsychosis = ifelse((iid == 443 & time_point == 3) |
                         (iid == 281 & time_point > 4.5), 1, clPsychosis),
    oSCZ = ifelse((iid == 443 & time_point == 3) |
                   (iid == 281 & time_point == 5), 1, oSCZ)
  )
##Consesus Lifetime Diagnosis
```


```{R}
FOR$round_age <- round(FOR$age)

table(FOR$round_age, FOR$ccMDD)

fid_group_list <- FOR_P %>%
  group_by(fid) %>%
  summarise(group = max(group, na.rm = TRUE), .groups = "drop")
# Step 2: Join back to the full FOR dataset
FOR <- FOR %>%
  left_join(fid_group_list, by = "fid")
table(FOR$group)
```


# Create my analytic now.
```{r}
setwd("C:/Users/hubshmz/Documents/Code/git/data")  # FORBOW computer
# setwd("C:/Users/zachh/Documents/Code/git/Data")  # Laptop
# setwd("C:/Users/zacha/Documents/RStudio/forbow/git/Data/ESCAP") # Tupper Windows Comp
# setwd("C:/Users/zacha/Documents/forbow/code/git") # Home Computer

write.csv(FOR, file = "analytic-zach.csv", row.names = FALSE)
```


```{r}



```






```{R}
look <- FOR %>% select(subject_id, 'time_point')

FOR <- FOR %>% filter(time_point < 97)

FOR$assessment_date[FOR$assessment_date == ""] <- NA  # Replace "" with NA
FOR$assessment_date <- as.Date(FOR$assessment_date) 



FOR$subject_id <- as.factor(FOR$subject_id)
FOR$assessment_date <- as.Date(FOR$assessment_date)

FOR <- FOR %>%
  arrange(subject_id) %>%
  mutate(
    group_index = (as.integer(subject_id) - 1) %/% 50 + 1,
    group_label = paste0("Group ", group_index)
  )

group_labels <- unique(FOR$group_label)

plot_list <- lapply(group_labels, function(grp) {
  df_grp <- FOR %>% filter(group_label == grp)
  
  p <- ggplot(df_grp, aes(x = assessment_date, y = time_point, group = subject_id, color = subject_id)) +
    geom_line() +
    geom_point(size = 2) +
    theme_minimal() +
    labs(
      title = paste("Participant Timepoints -", grp),
      x = "Assessment Date",
      y = "Timepoint",
      color = "Subject ID"
    )
  
  ggplotly(p)
})

plot_list[[15]]
```



##TOC
```{R}
# 1 "Major Depressive Disorder" ///
# 2 "Dysthymic Disorder" ///
# 3 "Mood Disorder NOS" ///
# 4 "Bipolar disorder I" ///
# 5 "Bipolar disorder II" ///
# 6 "Cyclothymic Disorder" ///
# 7 "Bipolar disorder NOS" ///
# 8 "Schizophrenia" ///
# 9 "Schizoaffective" ///
# 10 "Schizophreniform" ///
# 11 "Delusional Disorder" ///
# 12 "Brief Psychotic Disorder" ///
# 13 "Psychotic Disorder NOS" ///
# 14 "Psychotic disorder substance induced" ///
# 15 "Separation Anxiety" ///
# 16 "Specific Phobia" ///
# 17 "Social Phobia" ///
# 18 "Agoraphobia" ///
# 19 "Panic disorder" ///
# 20 "GAD" ///
# 21 "OCD" ///
# 22 "PTSD" ///
# 23 "Acute Stress" ///
# 24 "Anxiety Disorder NOS" ///
# 25 "Panic Attack" ///
# 26 "Enuresis" ///
# 27 "Encopresis" ///
# 28 "Anorexia Nervosa" ///
# 29 "Bulimia" ///
# 30 "Eating Disorder NOS" ///
# 31 "ADHD Combined" ///
# 32 "ADHD Inattentive" ///
# 33 "ADHD Hyperactive-Imp" ///
# 34 "ODD" ///
# 35 "Conduct Disorder" ///
# 36 "Tic Disorder Chronic" ///
# 37 "Tic Disorder Transient" ///
# 38 "Alcohol Abuse" ///
# 39 "Alcohol Dependence" ///
# 40 "Cannabis abuse" ///
# 41 "Cannabis dependence" ///
# 42 "Substance Abuse" ///
# 43 "Substance Dependence" ///
# 44 "Autistic Disorder" ///
# 45 "Aspergers Disorder" ///
# 46 "PDD NOS" ///
# 98 "Other Disorder" ///
# 99 "No response"


```


